---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
```{r libraries}
library(ggplot2)
```

## Loading and preprocessing the data

```{r}
unzip("activity.zip" )
data = read.csv("activity.csv")

```

## What is mean total number of steps taken per day?
```{r}
stepsByDay = tapply(data$steps, data$date, sum)

meanStepsByDay = mean(stepsByDay, na.rm = T)

meadianStepsByDay = median(stepsByDay, na.rm = T)

qplot(stepsByDay,xlab='Total steps per day', ylab='Frequency (binwith 500)', binwidth=500)

```

- Mean: `r meanStepsByDay`
- Median: `r meadianStepsByDay`


## What is the average daily activity pattern?

```{r}
stepsByInterval = aggregate(steps ~ interval, data, mean)

ggplot(data = stepsByInterval, aes(x=interval, y=steps)) + geom_line() + xlab("Interval") + ylab("average steps")

max = which.max(stepsByInterval$steps)

stepsByInterval[max,1]

```
The 5-minute interval that contains, on average across all the days in the dataset, the maximum number of steps is `r stepsByInterval[max,1]`

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
