---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
```{r libraries}
library(ggplot2)
library(Hmisc)
options(scipen=999)
```

## Loading and preprocessing the data

```{r}
unzip("activity.zip" )
data = read.csv("activity.csv")

```

## What is mean total number of steps taken per day?
```{r}
stepsByDay = tapply(data$steps, data$date, sum)

meanStepsByDay = mean(stepsByDay, na.rm = T)

meadianStepsByDay = median(stepsByDay, na.rm = T)

qplot(stepsByDay,xlab='Total steps per day', ylab='Frequency (binwith 500)', binwidth=500)

```

- Mean: `r meanStepsByDay`
- Median: `r meadianStepsByDay`


## What is the average daily activity pattern?

```{r}
stepsByInterval = aggregate(steps ~ interval, data, mean)

ggplot(data = stepsByInterval, aes(x=interval, y=steps)) + geom_line() + xlab("Interval") + ylab("average steps")

max = which.max(stepsByInterval$steps)



```
The 5-minute interval that contains, on average across all the days in the dataset, the maximum number of steps is `r stepsByInterval[max,1]`

## Imputing missing values

```{r}

nas = sum(!complete.cases(data))


```

The number of row with NAS is `r nas`

```{r}
imputedData = data 
imputedData$steps = impute(imputedData$steps, fun=mean)



imputedStepsByDay = tapply(imputedData$steps, imputedData$date, sum)

imputerdMeanStepsByDay = mean(imputedStepsByDay, na.rm = T)

imputedMeadianStepsByDay = median(imputedStepsByDay, na.rm = T)

meanDiff = imputerdMeanStepsByDay-meanStepsByDay

medianDiff = imputedMeadianStepsByDay - meadianStepsByDay

totalDiff = sum(imputedData$steps) - sum(data$steps, na.rm=T)  
  

qplot(imputedStepsByDay,xlab='Total steps per day', ylab='Frequency (binwith 500)', binwidth=500)

```  

- Mean: `r imputerdMeanStepsByDay`
- Median: `r imputerdMeanStepsByDay`

The difference between the mean of imputed and original data is `r meanDiff`  
The difference between the meadian of nimputed and original data is `r medianDiff`  
The difference of the sum of total steps from imputed and original data is `r totalDiff`  


## Are there differences in activity patterns between weekdays and weekends?

```{r}


imputedData$isWeekDay = as.factor(ifelse(as.POSIXlt(imputedData$date)$wd %in% seq(1,5), "weekday", "weekend"))

stepsByIntervalImputed = aggregate(steps ~ interval + isWeekDay, imputedData, mean)

ggplot(data = stepsByIntervalImputed, aes(x=interval, y=steps)) + 
    geom_line() + 
    facet_grid(isWeekDay ~ .) +
    xlab("interval") + 
    ylab("avarage  steps")

```
